---
title: "CCFRP Central California Fork Length and Total Length Comparison"
author: "Rachel Brooks"
date: '2023-03-17'
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, error=FALSE)

rm(list = ls());graphics.off()
library(tidyverse) # For data manipulation and summarization
library(plotrix) #To use standard error calculation
library(cowplot) #For grouping plots
library(scales) #For editing axis scales
library(rstatix) #For running ANCOVA
#library(ggpmisc) #adding equation and r2 to figures
library(here) ## for erin

alpha=0.5
formula<-y~x
theme_set(theme_classic(base_size=16))

```

Load Data

```{r}

length.data <-read.csv(here("Data", 'Fork-And-Total-Length-Data.csv'))
length.data.resolved <-read.csv(here("Data", 'Fork-And-Total-Length-Data-Resolved.csv'))


```
Blue/Deacon Rockfish

```{r blue deacon rf}

blue.deacon<-length.data%>%
  group_by(Institution, Species, Data.Source)%>%
  filter(Species == "Blue/Deacon Rockfish")

ggplot(blue.deacon, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Institution))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Blue/Deacon Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(blue.deacon, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Data.Source))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Blue/Deacon Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(blue.deacon, aes(x=Fork.Length..cm., y=Total.Length..cm.))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Blue/Deacon Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")
  
MOD <- lm(Total.Length..cm.~Fork.Length..cm., data = blue.deacon)
  summary(MOD)
  hist(MOD$residuals)

```

Black Rockfish

```{r black rf}

black<-length.data%>%
  group_by(Institution, Species, Data.Source)%>%
  filter(Species == "Black Rockfish")

ggplot(black, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Institution))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Black Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(black, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Data.Source))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Black Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(black, aes(x=Fork.Length..cm., y=Total.Length..cm.))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Black Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")
  
MOD <- lm(Fork.Length..cm.~Total.Length..cm., data = black)
  summary(MOD)
  hist(MOD$residuals)
  
```


Vermilion Rockfish

```{r vermilion rf}

vermilion<-length.data%>%
  group_by(Institution, Species, Data.Source)%>%
  filter(Species == "Vermilion Rockfish")

ggplot(vermilion, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Institution))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Vermilion Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(vermilion, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Data.Source))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Vermilion Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(vermilion, aes(x=Fork.Length..cm., y=Total.Length..cm.))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Vermilion Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")
  
MOD <- lm(Fork.Length..cm.~Total.Length..cm., data = vermilion)
  summary(MOD)
  hist(MOD$residuals)
  
```



Olive/Yellowtail Rockfish

```{r olive yellowtail rf}

olive.yellowtail<-length.data%>%
  group_by(Institution, Species, Data.Source)%>%
  filter(Species == "Olive/Yellowtail Rockfish")

ggplot(olive.yellowtail, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Institution))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Olive/Yellowtail Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(olive.yellowtail, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Data.Source))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Olive/Yellowtail Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(olive.yellowtail, aes(x=Fork.Length..cm., y=Total.Length..cm.))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Olive/Yellowtail Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")
  
MOD <- lm(Fork.Length..cm.~Total.Length..cm., data = olive.yellowtail)
#MOD2 <- lm(Total.Length..cm.~Fork.Length..cm., data = olive.yellowtail)
  summary(MOD)
  #summary(MOD2)
  hist(MOD$residuals)
  
```

Copper Rockfish

```{r copper rf}

copper<-length.data%>%
  group_by(Institution, Species, Data.Source)%>%
  filter(Species == "Copper Rockfish")

ggplot(copper, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Institution))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Copper Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(copper, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Data.Source))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Copper Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(copper, aes(x=Fork.Length..cm., y=Total.Length..cm.))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Copper Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")
  
MOD <- lm(Fork.Length..cm.~Total.Length..cm., data = copper)
  summary(MOD)
  hist(MOD$residuals)
  
```


Canary Rockfish

```{r canary rf}

canary<-length.data%>%
  group_by(Institution, Species, Data.Source)%>%
  filter(Species == "Canary Rockfish")

ggplot(canary, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Institution))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Canary Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(canary, aes(x=Fork.Length..cm., y=Total.Length..cm., col=Data.Source))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Canary Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")

ggplot(canary, aes(x=Fork.Length..cm., y=Total.Length..cm.))+
  geom_point()+
  geom_smooth(method = "lm")+ 
  ggtitle("Canary Rockfish") +
  xlab("Fork Length (cm)") + ylab("Total Length (cm)")
  
MOD <- lm(Fork.Length..cm.~Total.Length..cm., data = canary)
  summary(MOD)
  hist(MOD$residuals)
  
```

## Binning Addition
### E. Johnston 2023-03-19

Same comparisons, but binned in 2 cm length bins, similar to what M. Monk says happens for stock assessment purposes.


```{r data part II}

length_dat <- read_csv(here("Data", "Fork-And-Total-Length-Data3.csv"))
len_dat_resolved <- read_csv(here("Data", "Fork-And-Total-Length-Data-Resolved.csv"))

```


```{r data checks, echo = F, eval = F}
str(length_dat)
length_dat %>% arrange(desc(TL)) %>% slice(1)
length_dat %>% arrange(desc(FL)) %>% slice(1)
length_dat %>% arrange(TL) %>% slice(1)
length_dat %>% arrange(FL) %>% slice(1)


```

```{r bin data categories}
bin_dat <- len_dat_resolved %>%
  mutate(TL_bin = cut(TL, breaks = c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,
                                     32,34,36,38,40,42,44,46,48,50,52,54,56,58,60,
                                     62,64)),
         FL_bin = cut(FL, breaks = c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,
                                     32,34,36,38,40,42,44,46,48,50,52,54,56,58,60,
                                     62,64)),
         match = case_when(
           TL_bin == FL_bin ~ "YES",
           TL_bin != FL_bin ~ "NO"
         ))
```


```{r bin data categories check, echo = F, eval = F}
## checking out some numbers
# bin_dat %>% count(match)
# bin_dat %>% filter(Species == "Blue/Deacon Rockfish") %>% count(match)
# bin_dat %>% filter(!Species == "Canary Rockfish") %>% count(match)
# 
# ggplot(data = bin_dat)+
#   geom_bar(aes(x = TL_bin), fill = "Blue", alpha = 0.5)+
#   geom_bar(aes(x = FL_bin), fill = "Green", alpha = 0.5)

```


```{r bin data integers}

## the annoying long bin conversion

bin_dat_num <- bin_dat %>%
  mutate(TL_int = case_when(
    TL %in% c(11,12) ~ 12,
    TL %in% c(13,14) ~ 14,
    TL %in% c(15,16) ~ 16,
    TL %in% c(17,18) ~ 18,
    TL %in% c(19,20) ~ 20,
    TL %in% c(21,22) ~ 22,
    TL %in% c(23,24) ~ 24,
    TL %in% c(25,26) ~ 26,
    TL %in% c(27,28) ~ 28,
    TL %in% c(29,30) ~ 30,
    TL %in% c(31,32) ~ 32,
    TL %in% c(33,34) ~ 34,
    TL %in% c(35,36) ~ 36,
    TL %in% c(37,38) ~ 38,
    TL %in% c(39,40) ~ 40,
    TL %in% c(41,42) ~ 42,
    TL %in% c(43,44) ~ 44,
    TL %in% c(45,46) ~ 46,
    TL %in% c(47,48) ~ 48,
    TL %in% c(49,50) ~ 50,
    TL %in% c(51,52) ~ 52,
    TL %in% c(53,54) ~ 54,
    TL %in% c(55,56) ~ 56,
    TL %in% c(57,58) ~ 58,
    TL %in% c(59,60) ~ 60,
    TL %in% c(61,62) ~ 62,
    TL %in% c(63,64) ~ 64),
    FL_int = case_when(
      FL %in% c(11,12) ~ 12,
      FL %in% c(13,14) ~ 14,
      FL %in% c(15,16) ~ 16,
      FL %in% c(17,18) ~ 18,
      FL %in% c(19,20) ~ 20,
      FL %in% c(21,22) ~ 22,
      FL %in% c(23,24) ~ 24,
      FL %in% c(25,26) ~ 26,
      FL %in% c(27,28) ~ 28,
      FL %in% c(29,30) ~ 30,
      FL %in% c(31,32) ~ 32,
      FL %in% c(33,34) ~ 34,
      FL %in% c(35,36) ~ 36,
      FL %in% c(37,38) ~ 38,
      FL %in% c(39,40) ~ 40,
      FL %in% c(41,42) ~ 42,
      FL %in% c(43,44) ~ 44,
      FL %in% c(45,46) ~ 46,
      FL %in% c(47,48) ~ 48,
      FL %in% c(49,50) ~ 50,
      FL %in% c(51,52) ~ 52,
      FL %in% c(53,54) ~ 54,
      FL %in% c(55,56) ~ 56,
      FL %in% c(57,58) ~ 58,
      FL %in% c(59,60) ~ 60,
      FL %in% c(61,62) ~ 62,
      FL %in% c(63,64) ~ 64),
    Diff_int = TL_int -FL_int)

```


```{r same analyses as RB}

## Blue/Deacon rockfish

BLU_DEA <- bin_dat_num %>%
  filter(Species == "Blue/Deacon Rockfish")

mod_BLU <- lm(TL_int ~ FL_int, data = BLU_DEA)
summary(mod_BLU)

## Black rockfish

BLA <- bin_dat_num %>%
  filter(Species == "Black Rockfish")

mod_BLA <- lm(TL_int ~ FL_int, data = BLA)
summary(mod_BLA)

## Vermilion rockfish

VER <- bin_dat_num %>%
  filter(Species == "Vermilion Rockfish")

mod_VER <- lm(TL_int ~ FL_int, data = VER)
summary(mod_VER)

## Olive/Yellowtail rockfish

OYT <- bin_dat_num %>%
  filter(Species == "Olive/Yellowtail Rockfish")

mod_OYT <- lm(TL_int ~ FL_int, data = OYT)
summary(mod_OYT)

## Copper rockfish

CPR <- bin_dat_num %>%
  filter(Species == "Copper Rockfish")

mod_CPR <- lm(TL_int ~ FL_int, data = CPR)
summary(mod_CPR)

## Canary rockfish

CNY <- bin_dat_num %>%
  filter(Species == "Canary Rockfish")

mod_CNY <- lm(TL_int ~ FL_int, data = CNY)
summary(mod_CNY)


```

```{r same analyses as RB}

## Blue/Deacon rockfish


mod_BLU2 <- lm(TL ~ FL, data = BLU_DEA)
summary(mod_BLU2)

## Black rockfish


mod_BLA2 <- lm(TL ~ FL, data = BLA)
summary(mod_BLA2)

## Vermilion rockfish

mod_VER2 <- lm(TL ~ FL, data = VER)
summary(mod_VER2)

mod_VER3 <- lm(TL ~ FL*Institution, data = VER)
summary(mod_VER3)

## Olive/Yellowtail rockfish

mod_OYT2 <- lm(TL ~ FL, data = OYT)
summary(mod_OYT2)

OLV <- bin_dat_num %>%
  filter(Species == "Olive Rockfish")

YTL <- bin_dat_num %>%
  filter(Species == "Yellowtail Rockfish")

mod_OLV2 <- lm(TL ~ FL, data = OLV)
mod_YTL2 <- lm(TL ~ FL, data = YTL)

## Copper rockfish

mod_CPR2 <- lm(TL ~ FL, data = CPR)
summary(mod_CPR2)

## Canary rockfish

mod_CNY2 <- lm(TL ~ FL, data = CNY)
summary(mod_CNY2)

## Gopher rockfish

GPR <- bin_dat_num %>%
  filter(Species == "Gopher Rockfish")

mod_GPR2 <- lm(TL ~ FL, data = GPR)

## China rockfish

CHN <- bin_dat_num %>%
  filter(Species == "China Rockfish")

mod_CHN2 <- lm(TL ~ FL, data = CHN)

## Brown rockfish

BWN <- bin_dat_num %>%
  filter(Species == "Brown Rockfish")

mod_BWN2 <- lm(TL ~ FL, data = BWN)


## Rosy rockfish

RSY <- bin_dat_num %>%
  filter(Species == "Rosy Rockfish")

mod_RSY2 <- lm(TL ~ FL, data = RSY)

## Kelp rockfish

KLP <- bin_dat_num %>%
  filter(Species == "Kelp Rockfish")

mod_KLP2 <- lm(TL ~ FL, data = KLP)


```


```{r}

summary(mod_BLU2)
summary(mod_BLA2)
summary(mod_VER2)
summary(mod_OYT2)## didn't change
summary(mod_CPR2)
summary(mod_CNY2)
summary(mod_OLV2)
summary(mod_YTL2)
summary(mod_BWN2)
summary(mod_CHN2)
summary(mod_GPR2)
summary(mod_KLP2)
summary(mod_RSY2)


```


#### Theoretical Datasets

```{r theoretical data}

dummy_dat <- data.frame(FL = seq(11,63, by = 1))

## resolved equations
dummy_dat_calc <- dummy_dat %>%
  mutate(FL_mm = FL*10,
         TL_blu = 1.015561*FL + 0.488725,
         TL_bla = 1.01102*FL + 0.39437,
         TL_ver = 1.035447*FL - 0.450808,
         TL_olv = 1.03130*FL - 0.32448,
         TL_ytl = 1.02523*FL - 0.10160,
         TL_cpr = 1*FL - 5.802e-15,
         TL_cny = 1.049452*FL - 0.052804,
         TL_bwn = 0.984619*FL + 0.595875,
         TL_chn = 1*FL + 0,
         TL_gpr = 1.000258*FL + 0.002467,
         TL_klp = 1*FL + 0,
         TL_rsy = 0.97721*FL + 0.71181,
         e_TL_blu = 1.039*FL_mm + 2.495,
         e_TL_bla = 1.017*FL_mm + 1.595,
         e_TL_ver = 1.054*FL_mm - 7.857,
         e_TL_olv = 1.029*FL_mm + 1.419,
         e_TL_ytl = 1.025*FL_mm + 2.358,
         e_TL_cpr = 1.010*FL_mm + 0.629,
         e_TL_cny = 1.070*FL_mm - 4.107,
         e_TL_bwn = 1.007*FL_mm - 0.586,
         e_TL_chn = 1.001*FL_mm + 0.854,
         e_TL_gpr = 1.005*FL_mm - 0.759,
         #e_TL_klp = 1.070*FL_mm - 4.107, ## no kelp rockfish in echeverria
         e_TL_rsy = 1.015*FL_mm + 1.409,
         TL_blu = TL_blu*10,
         TL_bla = TL_bla*10,
         TL_ver = TL_ver*10,
         TL_olv = TL_olv*10,
         TL_ytl = TL_ytl*10,
         TL_cpr = TL_cpr*10,
         TL_cny = TL_cny*10,
         TL_bwn = TL_bwn*10,
         TL_chn = TL_chn*10,
         TL_gpr = TL_gpr*10,
         TL_klp = TL_klp*10,
         TL_rsy = TL_rsy*10)



## old not resolved equations
# dummy_dat_rb <- dummy_dat %>%
#   mutate(TL_blu = 1.011954*FL + 0.585388,
#          TL_bla = 1.00491*FL + 0.59292 ,
#          TL_ver = 1.037405*FL - 0.560013,
#          TL_oyt = 1.0255*FL - 0.1654,
#          TL_cpr = 1*FL + 6.355e-15,
#          TL_cny = 1.062201*FL - 0.359872)

## not going to bin anymore

# dummy_dat_bin <- dummy_dat %>%
#   mutate(TL_blu = 0.99990*FL + 0.89237,
#          TL_bla = 0.96440*FL + 1.89602,
#          TL_ver = 1.01327*FL + 0.33149,
#          TL_oyt = 0.99371*FL + 0.84570,
#          TL_cpr = 1*FL - 6.355e-15,
#          TL_cny = 1.059007*FL - 0.262025)

 #write_csv(dummy_dat_rb, path = here("Data", "dummy_dat_OG.csv"))
 #write_csv(dummy_dat_bin, path = here("Data", "dummy_dat_bin.csv"))


```


This table has FL 11-63 cm (the actual size ranges in our data) and the theoretical TL calculated based on linear regression output for real size measurements rounded to nearest whole cm, as is procedure for CCFRP.

```{r dummy dat rb, eval = F, echo = F}

dummy_dat_rb

```


This table has FL 11-63 cm and the theoretical TL calculated based on linear regression output for 2cm size bins, as they do for stock assessment purposes.

```{r dummy dat bin, eval = F, echo = F}
dummy_dat_bin

```


```{r}

## not combining olv and ytl anymore as per RS suggestions

# oyt_plot <- ggplot() +
#   geom_line(data = dummy_dat_rb, aes(x = FL, y = FL), linetype = "dashed")+
#   geom_line(data = dummy_dat_rb, aes(x = FL, y = TL_oyt), color = "red", size = 0.71)+
#   geom_line(data = dummy_dat_bin, aes(x = FL, y = TL_oyt), color = "blue", size = 0.71)+
#   labs(x = "\nFork Length (cm)", y = "Total Length (cm)\n", title = "Olive/Yellowtail Rockfish")+
#   theme(axis.title.x = element_text(size = 18),
#         axis.title.y = element_text(size = 18))

blu_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_blu), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_blu), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Blue/Deacon Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

bla_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_bla), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_bla), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Black Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

ver_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_ver), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_ver), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Vermilion Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

cpr_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_cpr), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_cpr), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Copper Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

cny_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_cny), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_cny), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Canary Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

olv_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_olv), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_olv), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Olive Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

ytl_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_ytl), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_ytl), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Yellowtail Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

bwn_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_bwn), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_bwn), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Brown Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

chn_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_chn), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_chn), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "China Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

gpr_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_gpr), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_gpr), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Gopher Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

klp_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_klp), color = "blue", size = 0.71)+
  #geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_klp), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Kelp Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))

rsy_plot <- ggplot() +
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = FL_mm), linetype = "dashed")+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = TL_rsy), color = "blue", size = 0.71)+
  geom_line(data = dummy_dat_calc, aes(x = FL_mm, y = e_TL_rsy), color = "red", size = 0.71)+
  labs(x = "\nFork Length (mm)", y = "Total Length (mm)\n", title = "Rosy Rockfish")+
  theme(axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18))




ggsave("olv_plot_resolved_echeverria.png", plot = olv_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("ytl_plot_resolved_echeverria.png", plot = ytl_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("blu_plot_resolved_echeverria.png", plot = blu_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("bla_plot_resolved_echeverria.png", plot = bla_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("ver_plot_resolved_echeverria.png", plot = ver_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("cpr_plot_resolved_echeverria.png", plot = cpr_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("cny_plot_resolved_echeverria.png", plot = cny_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("bwn_plot_resolved_echeverria.png", plot = bwn_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("chn_plot_resolved_echeverria.png", plot = chn_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("gpr_plot_resolved_echeverria.png", plot = gpr_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("klp_plot_resolved_echeverria.png", plot = klp_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))
ggsave("rsy_plot_resolved_echeverria.png", plot = rsy_plot, dpi = 1000, height = 5, width = 7, path = here("Output"))



```

